\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

%% Pointer to 'default' preamble
\input{../../thad_preamble.tex}

%% Header
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Documentation of rlmod using global g\\ }
\lhead{Research \\ 6/15/20}


\begin{document}
The purpose of this document is to record what was done to enable the \verb|rlmod| PST model(s) to use the structured global variable \verb|g| and other `clean up' actions taken. \\
Each paragraph describes the required changes to the PST file.

Initial globals:
\begin{verbatim}
%% Original globals block condensed into g...
global  rlmod_con n_rlmod rlmod_idx
global  rlmod_pot rlmod_st drlmod_st
global  rlmod_sig
\end{verbatim}

Modified globals:
\begin{verbatim}
global g
\end{verbatim}

%===============================================================================
\paragraph{rlm\_indx}
	\begin{itemize}
		\item Functionalized
		\item  Removed old globals, inserted g
		\item Prepened all relevant variables with g.rlmod.
	\end{itemize}

%===============================================================================
\paragraph{handleNewGlobals.m}
	\begin{itemize}
		\item Addition of if statement to properly handle legacy data inputs
	\end{itemize}

%===============================================================================
\paragraph{s\_simu\_Batch.m}
	\begin{itemize}
		\item accomodation for rlm\_indx functionalization
		\item prepended g.rlmod. to appropriate globals, logic checks, and state integrations.
	\end{itemize}

%===============================================================================
\paragraph{svm\_mgen\_Batch}
	\begin{itemize}
		\item added g.rlmod. to required globals, logic checks, state counters, and state populators.
	\end{itemize}

%===============================================================================
\paragraph{nc\_load}
	\begin{itemize}
		\item removal of old globals
		\item addition of g.rlmod. to Y matrix addtion
	\end{itemize}

%===============================================================================
\paragraph{ns\_file}
Should be functionalized...
	\begin{itemize}
		\item addition of g.rlmod. to globals for state alteration and state counters.
	\end{itemize}

%===============================================================================
\paragraph{p\_cont}
Should be functionalized...
	\begin{itemize}
		\item addition of g.rlmod. to globals for state distrubances and input signal logging.
	\end{itemize}

%===============================================================================
\paragraph{p\_file}
Should be functionalized...
	\begin{itemize}
		\item cleanup to rlmod call (removal of bus)
		\item addition of g.rlmod. to variables for state counting, d\_vector creation, derivative logging, and signal tracking.
	\end{itemize}

%===============================================================================
\paragraph{p\_m\_file}
Should be functionalized...
	\begin{itemize}
		\item Addition of g.rlmod to related variables for k\_col counting
	\end{itemize}

%===============================================================================
\paragraph{rlmod}

	\begin{itemize}
		\item updated internal function documentation
		\item appened g.rlmod. to appropriate variables
		\item removed unused globals
		\item Fixed incorrect call to non-existant variable (rl\_mod\_st)
	\end{itemize}

%===============================================================================
\paragraph{rlm\_indx}

	\begin{itemize}
		\item updated internal function documentation
		\item appened g.rlmod. to appropriate variables
		\item removed unused globals

	\end{itemize}

\end{document}
