\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

%% Pointer to 'default' preamble
\input{../../thad_preamble.tex}

%% Header
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Documentation of lmod using global g\\ }
\lhead{Research \\ 5/28/20}


\begin{document}
The purpose of this document is to record what was done to enable \verb|lmod| PST to use the structured global variable \verb|g| and other `clean up' actions taken.
Each paragraph describes the required changes the PST file that has anything to do with load modulation.

Initial globals:
\begin{verbatim}
%% load modulation variables
global lmod_con % defined by user
global n_lmod lmod_idx % initialized and created in lm_indx
global lmod_sig lmod_st dlmod_st % initialized in s_simu
global lmod_pot  % created/initialized in lmod.m 
% g.lmod.lmod_pot(:,1) = max, g.lmod.lmod_pot(:,2) = min
global lmod_data % added by Trudnowski - doesn't appear to be used?
% maybe in new models?
\end{verbatim}

Modified globals:
\begin{verbatim}
global g
\end{verbatim}

%===============================================================================
\paragraph{User Input Data File}
The `d\_xxx' file should now define \verb|lmod_con| as \verb|g.lmod.lmod_con|.
This is because in the `standard' PST method of operations, \verb|lmod_con| is defined as a global before the user data file is executed.
This effectively means that the user defined arrays in the data file are actually defining global arrays (who knew?).

Code has been added to handle if \verb|lmod_con| is not prepended with \verb|g.lmod|.
This approach may be simpler for backwards compatibility with `legacy' data sets.

%===============================================================================
\paragraph{ml\_sig.m}
User created file that defines signal(s) to load modulation.
Should include \verb|global g| and only receive index variable \verb|k|.
Utilize global time array located in \verb|g.sys.t|.

%===============================================================================
\paragraph{lm\_indx.m} % completed 
\ \\
Notes from file:
\begin{verbatim}
% syntax: f = lm_indx
% 5:02 PM 15/08/97
% determines the relationship between lmod and nc loads
% checks for lmod
% determines number of modulated loads
\end{verbatim}
Comments should be redone in a similar fashion as lmod.m

\begin{itemize}
\item Prepended \verb|g.lmod.| to appropriate globals:
\begin{enumerate}
\item \verb|n_lmod|
\item \verb|lmod_idx|
\end{enumerate}
\item Added comments for each code line.
\item Added check for \verb|lmod_con| field in \verb|g.lmod|. If not found, creates empty array and displays a message.
(empty array created as there may be other checks to see if \verb|lmod_con| is empty)
\end{itemize}

%===============================================================================
\paragraph{lmod.m}
This function calculates the initial state, and states of the lmod model.

\begin{itemize}
\item The beginning comments and function info was modified to more closely follow recommended function documentation as provided in the S.J. Chapman MATLAB book.

\item The function was modified to be a VOID function (i.e. return nothing).

\item \verb|bus| was removed from input parameters as it is not used.

\item Prepended all lmod related globals with \verb|g.lmod.|

\end{itemize}

%===============================================================================
\paragraph{s\_simu\_Batch.m}
\begin{itemize}
\item Added \verb|g.lmod.| to zero initializations of
	\begin{itemize}
		\item \verb|lmod_st|
		\item \verb|dlmod_st|
		\item \verb|lmod_sig|
	\end{itemize}
\item Added \verb|g.lmod.| to initialization call to lmod function 
\item Added \verb|g.lmod.| to check for live plot


\item Added \verb|g.lmod.| to integrations of 
	\begin{itemize}
		\item \verb|lmod_st| using \verb|dlmod_st|
	\end{itemize}

\item Added time array \verb|t| to \verb|g.sys.t|

\item Removed sending of \verb|bus| to lmod
\end{itemize}

%===============================================================================
\paragraph{nc\_load.m}
Adds load modulation to Y array.
\begin{itemize}
\item Added \verb|g.lmod.| to calls to \verb|lmod_idx| and \verb|lmod_st|.
\end{itemize}

%===============================================================================
\paragraph{svm\_mgen\_Batch.m} \ \\
Modified, not tested...

%===============================================================================
\paragraph{ns\_file.m} \ \\
Called from \verb|svm_mgen| $\therefore$ not modified.

%===============================================================================
\paragraph{p\_cont.m} \ \\
Invoked during linearization of system $\therefore$ not modified.

%===============================================================================
\paragraph{p\_file.m} \ \\
Associated file with svm\_mgen - i.e. state space model stuff $\therefore$ not modified.



\end{document}
