\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

%% Pointer to 'default' preamble
\input{../../thad_preamble.tex}

%% Header
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Research Update \\ Week of May 25th, 2020}
\lhead{Research \\ }


\begin{document}
\begin{multicols}{2}
\raggedright

\paragraph{Recent Progress:}
	\begin{enumerate}
		\itemsep0em 
		\item Stajcar and Trudnowski code acquired. \\ 
		Modified to run from repository folders
		\item New example cases verified as working:
		\begin{itemize}
			\item Load step using lmod
		\end{itemize}
		\item octaveComp created - Automatically runs from s\_simu\_Batch if Octave is detected. Handles execution of compatibility commands and package loadings.
		
		\item Cases verified as working in Octave:
				\begin{itemize}
					\itemsep0em 
					\footnotesize
					\item OneMacInfBus fault
					\item genModelTest
					\item PSTexample system line fault
					\item pwrmod-Pinjection (Example1)
					\item pwrmod-Iinjection (Example2)
					\item ivmmod- (Example1)
				\end{itemize}
		
		\item GitHub created and updated:\\
	{\footnotesize	\verb|https://github.com/thadhaines/MT-Tech-SETO| }\\
	\end{enumerate}
	

	
\paragraph{Current Tasks:}
	\begin{enumerate}
		\itemsep 0em 
		\item Look at Trudnowski code for `structured array, functionalized' approach.
		\item Look at Stajcar code for basic transient stability simulation flow.
		\item Work on understanding PST
		\item Document findings of PST functionality
		\item Investigate Octave compatibility
		\item Create modulation case: ramp/noise 
		\item Continue to collect example cases
		\item Continue to work on data plots 
\end{enumerate}

\paragraph{Possible Future Tasks:} % Maybe good ideas?
	\begin{enumerate}
		\item Investigate Sandia integrator stability methods.	
		\item See if the modified PST used by Sandia in 2015 paper exists for an example of how they implemented different integration routines / stability calculations.	
	\end{enumerate}

\vfill\null
\columnbreak

\paragraph{Coding Thoughts:} 
	\begin{enumerate}

		\itemsep 0em 
		\item Condense $\approx$340 globals into 1 structured array with $\approx$18 fields based on category that contain PST arrays used for vector calculations.
		\item Enable `objects' (structure of arrays), but include functions to interact with condensed globals so vectorized operations are still possible.\\
		This requires more conceptual modeling to understand what needs to be passed/references/changed for each `object'.
		\item Separate total system calculation of derivatives into scripts/functions to allow for easier changing of integration method.
		Possibly employ \verb|feval| for a more dynamic calculation routine.
		\item Rework how switching/perturbance events are handled into a more flexible and general format.
		\item Generate something similar to unit test cases to verify code changes don't break everything during refactor.
		\item Generate comparison scripts to verify simulated results match after code changes.
	\end{enumerate}
	


\paragraph{Current Questions:}
	\begin{enumerate}
	\itemsep0em 
\item Which version of PST to start with?
\item How closely does actual work follow TWP?
		\item Minimum requirements for system case?
\begin{minipage}{\linewidth}
\begin{multicols}{2}
		\begin{itemize}
\itemsep0em 
		\footnotesize
			\item Load flow solver
			\item Network solver
			\item Machine models
			\item Governor model
			\item Exciter models
			\item pwrmod models
			\item ivmmod model
			\item load modulation models
			\item ...
		\end{itemize}
\end{multicols}
\end{minipage}

		\item PST modeling of transformers?
		\item PST modeling of faults: \\
		Uses alternate Y matrices? \\
		Creates fault bus?
	\end{enumerate}



\vfill\null
\end{multicols}



\begin{comment}
% Unused categories
\paragraph{Future Tasks:} %(Little to No Progress since last time / Things coming down the pipe)
	\begin{enumerate}
		\item none		
	\end{enumerate}
	
\paragraph{Future Work: (not by me)}
	\begin{itemize}
		\item none
	\end{itemize}

\paragraph{Requests:}
	\begin{enumerate}
			\item none
	\end{enumerate}
\end{comment}



\end{document}