\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

%% Pointer to 'default' preamble
\input{../../thad_preamble.tex}

%% Header
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Research Update \\ Week of July 8th, 2020}
\lhead{Research \\ }


\begin{document}
\begin{multicols}{2}
\raggedright

\paragraph{Recent Progress:}
	\begin{enumerate}
		\itemsep0em 
		\item Global g, linear \& non-linear functionality for:
		\begin{minipage}{\linewidth}
		%\begin{multicols}{2}
				\begin{itemize}
		\itemsep0em 
				\footnotesize
					\item system variables
					\item non-conforming loads
				\end{itemize}
		%\end{multicols}
		\end{minipage}
		%\item Added Exciter models 0-4 to global g, tested as functional in both linear and non-linear batch runs.
		%\item Added Syncrhonous machine models em, sub, tra, and sub\_NEW to global g, tested as functional in both linear and non-linear batch runs.
	%	\item Conceptual work on \verb|lmon| - a line flow montior for non-linear simulation
		%\item Collected thoughts on AGC.
		%\item Started work on batch unit testing
		\item ODE test for variable time step
		\item Found note about PSS gain - Same as Ryan info.
		
		\item created MATLAB plot functions to compare PST data
		\item GitHub updated:\\
	{\footnotesize	\verb|https://github.com/thadhaines/MT-Tech-SETO| }\\
	\end{enumerate}
	

\paragraph{Sandia Action Items:}
	\begin{itemize}
		\itemsep 0em 
			\item Continue development of pwrmod and ivmmod models and their implementation in PST.
			%\item Be aware of multi rate methods % mostly TAMU/Power world
			\item Decide on PST base version (3.1$\longrightarrow$SETO)
			\item Plan for variable time step methods
			\item Investigate power electronics-based models (REGC - Matt)
	\end{itemize}

	
\paragraph{Current Tasks:}
	\begin{enumerate}
		\itemsep 0em 
		\item Continue to cast globals to structured g
		\item Test models in both non-linear and linear simulations
		\item Explore/Create example cases
		\item Get code/cases from Ryan
		\item Think about AGC implementation.
		\item Think about using standard ODE solvers
		\item think about cleaning up or flowcharting svm\_mgen\_Batch
		%\item Reference Trudnowski code for `structured array, functionalized' approach.
		%\item Reference Stajcar code for basic transient stability simulation flow.
		\item Work on understanding PST operation
		\item Document findings of PST functionality
		\item Investigate Octave compatibility
\end{enumerate}

\vfill\null
\columnbreak

\paragraph{Possible Future Tasks:} % Maybe good ideas?
	\begin{enumerate}
		\item Investigate Sandia integrator stability methods.	
		See if the modified PST used by Sandia in 2015 paper exists for an example of how they implemented different integration routines / stability calculations.	
	\end{enumerate}


\paragraph{Coding Thoughts:} 
	\begin{enumerate}

		\itemsep 0em 
		\item Condense $\approx$340 globals into 1 structured array with $\approx$18 fields based on category that contain PST arrays used for vector calculations. ex: \verb|g.lmod.lmod_con|, \verb|g.sys.t|
		\item Enable `objects' (structure of arrays), but include functions to interact with condensed globals so vectorized operations are still possible.\\
		This requires more conceptual modeling to understand what needs to be passed/references/changed for each `object'.
		Would enable addition of area definitions to models.
		\item Separate total system calculation of derivatives into scripts/functions to allow for easier changing of integration method.
		Possibly employ \verb|feval| for a more dynamic calculation routine.
		\item Rework how switching \& perturbance events are handled into a more flexible and general format. (use flags)
		\item Generate something similar to unit test cases to verify code changes don't break everything during refactor.
		\item Generate comparison scripts to verify simulated results match after code changes.
	\end{enumerate}
	


\paragraph{Current Questions:}
	\begin{enumerate}
	\itemsep0em 
	\item Requirements for variable step methods
	\item PST modeling of transformers?
	\end{enumerate}



\vfill\null
\end{multicols}



\begin{comment}
		\item PST modeling of faults: \\
		Uses alternate Y matrices? \\
		Creates fault bus?

Things required for simulation....
\begin{minipage}{\linewidth}
\begin{multicols}{2}
		\begin{itemize}
\itemsep0em 
		\footnotesize
			\item system model
			\item Load flow solver
			\item Network solver
			\item Machine models
			\item Governor model
			\item Exciter models
			\item converter models
			\item load modulation models
			\item ...
		\end{itemize}
\end{multicols}
\end{minipage}

% Unused categories
\paragraph{Future Tasks:} %(Little to No Progress since last time / Things coming down the pipe)
	\begin{enumerate}
		\item none		
	\end{enumerate}
	
\paragraph{Future Work: (not by me)}
	\begin{itemize}
		\item none
	\end{itemize}

\paragraph{Requests:}
	\begin{enumerate}
			\item none
	\end{enumerate}
\end{comment}



\end{document}