\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

%% Pointer to 'default' preamble
\input{../../thad_preamble.tex}

%% Header
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Research Update \\ Week of May 19th, 2020}
\lhead{Research \\ }


\begin{document}
\begin{multicols}{2}
\raggedright

\paragraph{Recent Progress:}
	\begin{enumerate}
		\itemsep0em 
		\item Office keys acquired
		\item Lit review sent to Dave
		\item PST not included with Graham's book 
		\item Joe Chow has PST and user manual available for download from his site.
		\\ i.e. PST seems pretty free.
		\item PST folder `cleaned up'
		\item s\_simu\_Batch `cleaned up'
		\item Running PST comments are being collected in Examples folder readme. \\ (for now)
		\item Example cases verified as working:
		\begin{itemize}
			\item EELE 5550 machine comparisons
			\item One machine infinite Bus line trip
			\item PST user manual system with 3 phase fault
			\item Power mod using both Current and Power injection plus linearizion.
			\item IVM mod example
		\end{itemize}
		\item IVM mod example verified as working in GNU Octave
		\item Reached out to Sam for PST examples
		\item GitHub created and updated:\\
	{\footnotesize	\verb|https://github.com/thadhaines/MT-Tech-SETO| }\\
	\end{enumerate}
	
\vfill\null
\columnbreak
	
\paragraph{Current Tasks:}
	\begin{enumerate}
		\itemsep0em 
		\item Work on understanding PST
		\item Document findings of PST functionality
		\item Think of ways to `objectify' PST
		\item Create modulation case \\ ramp/step/noise 
		\item Add logging of loads
		\item Continue to work on data plots 
		\item Continue to collect example cases
\end{enumerate}

\paragraph{Current Questions:}
	\begin{enumerate}
	\itemsep0em 
		\item Minimum requirements for system case?
		\begin{itemize}
			\item Load Flow Solver
			\item Network Solver
			\item Machine models
			\item Governor model
			\item Exciter models
			\item pwrmod models
			\item ivmmod model
			\item load modulation model
			\item ...
		\end{itemize}
		\item PST modeling of transformers?
		\item PST modeling of faults? \\
		Uses alternate Y matrices? \\
		Creates fault bus?
	\end{enumerate}

\paragraph{Possible Future Tasks:} % Maybe good ideas?
	\begin{enumerate}
		\item Investigate Sandia integrator stability methods.		
	\end{enumerate}

\vfill\null
\end{multicols}



\begin{comment}
% Unused categories
\paragraph{Future Tasks:} %(Little to No Progress since last time / Things coming down the pipe)
	\begin{enumerate}
		\item none		
	\end{enumerate}
	
\paragraph{Future Work: (not by me)}
	\begin{itemize}
		\item none
	\end{itemize}

\paragraph{Requests:}
	\begin{enumerate}
			\item none
	\end{enumerate}
\end{comment}



\end{document}