\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

%% Pointer to 'default' preamble
\input{../../thad_preamble.tex}

%% Header
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Research Update \\ Week of August 19th, 2020}
\lhead{Research \\ }

\usepackage[hidelinks]{hyperref} % allow links in pdf
%\href{https://digitalcommons.mtech.edu/grad_rsch/242/}{Long-Term Dynamic Simulation of Power Systems using Python, \\Agent Based Modeling, and Time-Sequenced Power Flows}
\begin{document}
\begin{multicols}{2}
\raggedright

\paragraph{Recent Progress:}
\begin{comment}

		\itemsep0em 
		\item Added to global g and VTS:
		\begin{minipage}{\linewidth}
				%\begin{multicols}{2}
						\begin{itemize}
				\itemsep0em 
						\footnotesize
							\item ivmmod
							\item pwrmod
						\end{itemize}
				%\end{multicols}
				\end{minipage}
		\item\href{https://github.com/thadhaines/MT-Tech-SETO/blob/master/researchDocs/TEX/one-offs/200804-VTSexplained/200804-VTSexplained.pdf}{Updated VTS documentation}
		\item\href{https://github.com/thadhaines/MT-Tech-SETO/blob/master/researchDocs/TEX/one-offs/200806-ExtendedVersionComp/200806-ExtendedVersionComp.pdf}{Created 4 minute simulation showing VTS is $\approx$14x faster than PST 3.1.1}
		\item\href{https://github.com/thadhaines/MT-Tech-SETO/blob/master/researchDocs/TEX/one-offs/200806-ExtendedVTSdetail/200806-ExtendedVTSdetail.pdf}{Created a document showing possible VTS switching issues.}
		\item `Single Time Block' idea tested - not viable due to MATLAB solver operations.
		\item \href{https://github.com/thadhaines/MT-Tech-SETO/blob/master/researchDocs/TEX/one-offs/200709-PSTsetoVersionChanges/200709-PSTsetoVersionChanges.pdf}{Updated pst SETO change doc}
		\item \href{https://github.com/thadhaines/MT-Tech-SETO/blob/master/researchDocs/TEX/one-offs/200811-IVMwithVTS/200811-IVMwithVTS.pdf}{Tested IVM in VTS, created result doc.}
\end{comment}
	\begin{enumerate}	
		\item Added license to code repository
		\item Corrected PWRMOD handling of states in VTS
		\item Refined VTS order of operations and time vector
		\item \href{https://github.com/thadhaines/MT-Tech-SETO/blob/master/researchDocs/TEX/one-offs/200817-AGCminiWECC10min/200817-AGCminiWECC10min.pdf}{Created MiniWECC AGC results for Pload Step}
		\item Added handling of generator trip to AGC H and F calcs
		\item \href{https://github.com/thadhaines/MT-Tech-SETO/blob/master/researchDocs/TEX/one-offs/200818-AGCminiWECCgenTrips/200818-AGCminiWECCgenTrips.pdf}{Created MiniWECC AGC results for Gen Trips}
		\item Updated PST to version 4.0.0-a4
		
		%\item Added Exciter models 0-4 to global g, tested as functional in both linear and non-linear batch runs.
		%\item Started work on batch unit testing
		%\item ODE test for variable time step\
		%\item Found example for SVC - shows version difference between 2 and 3 - possibly due to \verb|exc_dc12| model.
		%\item Created more MATLAB plot functions to compare PST data

		\item \href{https://github.com/thadhaines/MT-Tech-SETO}{GitHub updated:}\\
	{\footnotesize \verb|https://github.com/thadhaines/MT-Tech-SETO| }\\
	\item Employment ``good'' till 09/18/20
	\end{enumerate}

\paragraph{Current Tasks:}
	\begin{enumerate}
		\itemsep 0em 
	\item Create long term event (with pwrmod)
	\item Verify VTS operation
		\item Refine VTS documentation	
		\item Work for PST 4.0.0:
		\begin{itemize}
		\footnotesize
		\itemsep0em
		\item Verify and Validate operation of AGC, PWRMOD, IVMMOD, and VTS.
		\item Clean up examples
		\item Clean up code comments
		\item Clean up readme files
		\end{itemize}
		\item Work on understanding PST operation
		\item Document findings of PST functionality
		\item Investigate Octave compatibility
\end{enumerate}

\paragraph{Action Items From Sandia:}
	\begin{itemize}
		\itemsep 0em 
		%	\item Continue development of pwrmod / ivmmod models and their implementation in PST.
			%\item Be aware of multi rate methods % mostly TAMU/Power world
		%	\item Decide on PST base version (3.1$\longrightarrow$SETO$\longrightarrow$4.0)
			\item Run long term simulation to show benefits of VTS.
		%	\item Allow them to duplicate work.
	\end{itemize}
	

\vfill\null
\columnbreak

\paragraph{Coding Thoughts:} 
	\begin{enumerate}

		\itemsep 0em 
	%	\item Condense $\approx$340 globals into 1 structured array with $\approx$18 fields based on category.
	%	\item Create new \verb|s_simu_Batch| style script that functionalizes the newtork and dynamic calculations so that standard MATLAB ODE solvers may be used.
		%\item Enable `objects' (structure of arrays), but include functions to interact with condensed globals so vectorized operations are still possible.\\
	%	This requires more conceptual modeling to understand what needs to be passed/references/changed for each `object'.
	%	Would enable addition of area definitions to models.
	%	\item Separate total system calculation of derivatives into scripts/functions to allow for easier changing of integration method.
	%	Possibly employ \verb|feval| for a more dynamic calculation routine.
		\item Rework how switching \& perturbance events are handled into a more flexible and general format. (flags? objects?)
%		\item Generate something similar to unit test cases to verify code changes don't break everything during refactor.
		\item Generate comparison scripts to verify simulated results match after code changes.
		

	\end{enumerate}



\paragraph{Current Questions:}
	\begin{enumerate}
	\itemsep0em 
	
	
%	\item Induction machines have no speed?\\ only angle?
%	\item PST modeling of transformers?
	\item Play in data for variable solar irradiance? (Slow Sine with step events for clouds.)
%	\item PSS design doesn't seem to be used in normal simulation?
%	\item Deadlines of any sort?
	
	\end{enumerate}	

\paragraph{Loose ends:} % Random stuff that will be left undone...
	\begin{enumerate}
	\item As infinite buses don't seem to be used in dynamic simulation, they were not converted to use the golbal g.
		\item \verb|tgh| model not converted for use with global g. (no examples of tgh gov)
		\item In original \verb|s_simu_Batch|, the global \verb|tap| value associated with HVDC is over-written with  a value used to compute line current multiple times.
		\item Constant Power or Current loads seem to require a portion of constant Impedance.
		\item PSS design functionality not explored
		\item No examples of of delta P omega filter or user defined damping controls for SVC and TCSC models
		\item Differences in \verb|mac_ind| between pst 2 and 3. Seem backward compatible - untested.
		\item A tripped generators inertia should be removed from total inertia calculations of average frequency used in the AGC model.
	\end{enumerate}
\vfill\null

\end{multicols}



\begin{comment}
	\item Global g,non-linear functionality added for: %  linear \& 
		\begin{minipage}{\linewidth}
		\begin{multicols}{2}
				\begin{itemize}
		\itemsep0em 
				\footnotesize
				\raggedright
					\item g.k
					\item g.vts
				\end{itemize}
		\end{multicols}
		\end{minipage}


\paragraph{Possible Future Tasks:} % Maybe good ideas?
	\begin{enumerate}
		\item Investigate Sandia integrator stability methods.	
		See if the modified PST used by Sandia in 2015 paper exists for an example of how they implemented different integration routines / stability calculations.	
	\end{enumerate}



		\item PST modeling of faults: \\
		Uses alternate Y matrices? \\
		Creates fault bus?

Things required for simulation....
\begin{minipage}{\linewidth}
\begin{multicols}{2}
		\begin{itemize}
\itemsep0em 
		\footnotesize
			\item system model
			\item Load flow solver
			\item Network solver
			\item Machine models
			\item Governor model
			\item Exciter models
			\item converter models
			\item load modulation models
			\item ...
		\end{itemize}
\end{multicols}
\end{minipage}

% Unused categories
\paragraph{Future Tasks:} %(Little to No Progress since last time / Things coming down the pipe)
	\begin{enumerate}
		\item none		
	\end{enumerate}
	
\paragraph{Future Work: (not by me)}
	\begin{itemize}
		\item none
	\end{itemize}

\paragraph{Requests:}
	\begin{enumerate}
			\item none
	\end{enumerate}
\end{comment}



\end{document}